A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-29 03_smoothing_tracks.Rmd

```{r}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot()+
  geom_point(data = data_errors,
             aes(x, y),
             col = pal[3],
             size = 0.2, alpha = 0.5)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            lwd = 0.5)+          
  geom_path(data = data_plot,
            aes(x, y,
                col = window_size,
                group = window_size),
            show.legend = F,
            lwd = 0.5)+
  coord_equal(expand = F,
              ylim = c(0.6, 0.85),
              xlim = c(NA, 2.3),
              ratio = 1.75)+
  annotate(geom = "text",
           x = c(0.75, seq(1.1, 2, length.out = 4)),
           y = 0.82,
           label = sprintf("(%s)", letters[seq(5)]),
           fontface = "bold")+
  scale_colour_distiller(palette = "BuPu", direction = 1,
                         values = c(-0.5, 1))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())

@@

```{r}
### plot figures
fig_agg_data <- 
  lapply(list_of_agg, function(df) {
    ggplot(df)+
      geom_point(data = data_agg,
                 aes(x, y),
                 size = 0.2,
                 col = pal[3])+
      geom_path(aes(x,y), 
                col = pal[1])+
      geom_point(aes(x,y, 
                     size = SD,
                     fill = SD,
                     group = interval),
                 shape = 21,
                 alpha = 0.8,
                 show.legend = F)+
      scale_fill_distiller(palette = "Purples", direction = 1,
                           values = c(-0.25, 1))+
      scale_size(range = c(2, 4))+
      ggthemes::theme_few()+
      theme(axis.text = element_blank(),
            axis.title = element_blank(),
            panel.background = element_rect(fill = "white"))+
      coord_cartesian(ylim = c(0.6, NA))
  })
```

@@

```{r}
# now plot distribution of speed
data_agg <- rbindlist(list_of_agg)

# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_hline(yintercept =
               1 + quantile(data$speed, na.rm = T,
                        probs = c(0.5, 0.95)),
             lty = c(1, 2))+
  geom_errorbar(data = speed_agg_smooth,
                aes(x = factor(interval),
                    ymin = 1 + median - sd,
                    ymax = 1 + median + sd),
                width = 0.2,
                position = position_nudge(x = 0.25)) +
  geom_point(data = speed_agg_smooth,
             aes(x = factor(interval),
                 y = 1 + median),
             shape = 21,
             size = 3,
             fill = pal[3],
             position = position_nudge(x = 0.25)) +
  geom_boxplot(aes(factor(interval), 1 + speed),
               position = position_nudge(x = -0.25,),
               fill = "grey",
               alpha = 0.5,
               show.legend = F, 
               width = 0.25, 
               outlier.size = 0.2)+
  scale_y_log10(label = scales::comma,
                limits = c(NA, 1.005))+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```

```{r}
# make combined figure
fig_aggregate <-
  wrap_plots(append(fig_agg_data[3:4], list(fig_agg_speed)),
             design = "AABBC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))

>>>>

```{r echo=FALSE}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot()+
  geom_point(data = data_errors,
             aes(x, y),
             col = pal[3],
             size = 0.2, alpha = 0.5)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            lwd = 0.5)+          
  geom_path(data = data_plot,
            aes(x, y,
                col = window_size,
                group = window_size),
            show.legend = F,
            lwd = 0.5)+
  coord_equal(expand = F,
              ylim = c(0.6, 0.85),
              xlim = c(NA, 2.3),
              ratio = 1.75)+
  annotate(geom = "text",
           x = c(0.75, seq(1.1, 2, length.out = 4)),
           y = 0.82,
           label = sprintf("(%s)", letters[seq(5)]),
           fontface = "bold")+
  scale_colour_distiller(palette = "BuPu", direction = 1,
                         values = c(-0.5, 1))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())

@@

```{r echo=FALSE}
### plot figures
fig_agg_data <- 
  lapply(list_of_agg, function(df) {
    ggplot(df)+
      geom_point(data = data_agg,
                 aes(x, y),
                 size = 0.2,
                 col = pal[3])+
      geom_path(aes(x,y), 
                col = pal[1])+
      geom_point(aes(x,y, 
                     size = SD,
                     fill = SD,
                     group = interval),
                 shape = 21,
                 alpha = 0.8,
                 show.legend = F)+
      scale_fill_distiller(palette = "Purples", direction = 1,
                           values = c(-0.25, 1))+
      scale_size(range = c(2, 4))+
      ggthemes::theme_few()+
      theme(axis.text = element_blank(),
            axis.title = element_blank(),
            panel.background = element_rect(fill = "white"))+
      coord_cartesian(ylim = c(0.6, NA))
  })
```

@@

```{r}
# now plot distribution of speed
data_agg <- rbindlist(list_of_agg)
```

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_hline(yintercept =
               1 + quantile(data$speed, na.rm = T,
                        probs = c(0.5, 0.95)),
             lty = c(1, 2))+
  geom_errorbar(data = speed_agg_smooth,
                aes(x = factor(interval),
                    ymin = 1 + median - sd,
                    ymax = 1 + median + sd),
                width = 0.2,
                position = position_nudge(x = 0.25)) +
  geom_point(data = speed_agg_smooth,
             aes(x = factor(interval),
                 y = 1 + median),
             shape = 21,
             size = 3,
             fill = pal[3],
             position = position_nudge(x = 0.25)) +
  geom_boxplot(aes(factor(interval), 1 + speed),
               position = position_nudge(x = -0.25,),
               fill = "grey",
               alpha = 0.5,
               show.legend = F, 
               width = 0.25, 
               outlier.size = 0.2)+
  scale_y_log10(label = scales::comma,
                limits = c(NA, 1.005))+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(append(fig_agg_data[3:4], list(fig_agg_speed)),
             design = "AABBC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))

### 2020-10-29 05_calibration_data.Rmd

```{r}
# read and plot example data
data <- fread("data/atlas1060_allTrials_annotated.csv")
data_raw <- copy(data)

# plot data
fig_data_raw <-
  ggplot(data)+
  geom_path(aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(aes(x, y),
             col = pal[3], alpha = 0.2, size = 2)+
  ggthemes::theme_map()+
  coord_sf(crs = 32631)

@@

Plot the result.

```{r}
# plot data
fig_data_bbox <-
  ggplot()+
  geom_path(data = data_raw,
            aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(data = data_raw,
             aes(x, y,
                 col = x > 645000),
             alpha = ifelse(data_raw$x > 645000, 0.5, 1),
             size = ifelse(data_raw$x > 645000, 0.3, 2),
             show.legend = F)+
  scale_colour_manual(values = c("grey", pal[3]))+
  geom_vline(xintercept = 645000,
             col = "grey", lty = 2)+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631)

@@

```{r}
# plot filtered data
fig_speed_outliers <-
  ggplot()+
  geom_point(data = data,
             aes(x, y, 
                 col = speed_in < 25.6),
             size = 0.3, alpha = 0.5,
             show.legend = F)+
  scale_color_manual(values = c("grey", pal[3]))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "speed (m/s)")

@@

@@

```{r}
# make figure
# fig_smooth <-
#   ggplot()+
#   geom_path(data = data,
#              aes(x, y),
#             col = RColorBrewer::brewer.pal(4, "Set1")[4])+
#   annotate(geom = "rect",
#            xmin = c(650785, 650045),
#            ymin = c(5904450, 5902700),
#            xmax = c(652500, 650682),
#            ymax = c(5906133, 5903080),
#            fill = "grey90",
#            alpha = 0.5,
#            col = NA)+
#     annotate(geom = "text",
#            x = c(650785, 650045) + 400,
#            y = c(5904450, 5902700) + 300,
#            col = "black",
#            label = c("d", "e"))+
#   theme_void()+
#   coord_sf(crs = 32631)+
#   labs(colour = "track")

# make zoomed in figures
fig_inset <- mapply(function(xl, yl) {
  ggplot()+
    geom_point(data = data_raw[!data_unproc, on = c("x", "y")],
               aes(x, y),
               col = "grey",
               shape = 4,
               size = 0.4)+
    geom_point(data = data_unproc,
               aes(x, y),
               col = pal[3],
               shape = 19, 
               alpha = 0.5)+
    geom_path(data = data,
              aes(x, y),
              col = RColorBrewer::brewer.pal(4, "Set1")[4])+
    ggthemes::theme_few()+
    theme(axis.title = element_blank(),
          axis.text = element_blank())+
    ggspatial::annotation_scale(location = "br")+
    coord_cartesian(
             xlim = xl,
             ylim = yl, expand = F
             )+
    labs(colour = "track")
}, list(xl1 = c(650785, 653250),
        xl2 = c(650045, 650682)),
   list(yl1 = c(5904450, 5906133),
        yl2 = c(5902700, 5903080)),
SIMPLIFY = FALSE)

@@

```{r}
# make combined walkthrough figure
figure_walkthrough <-
wrap_plots(
  list(
    fig_data_bbox, fig_speed_outliers, fig_median_smooth),
  design = "AB\nAC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")&
  theme(plot.tag = element_text(face = "bold"))

@@

@@

```{r}
fig_calib_residence <-
  ggplot()+
  geom_point(data = data_res, 
             aes(x, y),
             size = 5, shape = 2,
             alpha = 0.1)+
  geom_point(data = data_recurse,
             aes(x, y, 
                 col = res_time > 5,
                 size = res_time > 5),
             shape = 19, alpha = 0.4,
             show.legend = F)+
  geom_path(data = data_recurse,
             aes(x, y),
            col = "grey", lwd = 0.2)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_size_manual(values = c(0.5, 2))+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631)
```

@@

### Plot the outcome

```{r}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             # stroke = ,
             col = "grey20",
             alpha = 1)+
    # geom_path(data = data_recurse,
    #          aes(x, y),
    #         col = "grey", lwd = 0.2)+
  # geom_text(data = data_res_summary,
  #           aes(x_median, y_median,
  #               label = tID),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = 100,
  #           fontface = "bold",
  #           col = "grey20",
  #           alpha = 1)+
  # geom_text(data = patch_summary_data, 
  #           aes(x_median, y_median,
  #               label = patch),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = -50,
  #           fontface = "bold",
  #           col = pal[4],
  #           alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  # geom_segment(data = patch_summary_data,
  #           aes(x = x_end, y = y_end,
  #               xend = shift(x_start, type = "lag"),
  #               yend = shift(y_start, type = "lag")),
  #           col = pal[4], lty = 1,
  #           lwd = 0.5)+
  # geom_point(data = patch_summary_data,
  #            aes(x_median, y_median),
  #            size = 5,
  #            stroke = 1,
  #            col = pal[4],
  #            shape = 1,
  #            show.legend = F)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```

@@

```{r}
# make figure comparing different methods
figure_patch_duration <-
  ggplot()+
  geom_point(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             show.legend = F,
            size = 3,
            stroke = 2,
            shape = 1,
            col = pal[2])+
  geom_smooth(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             se = F,
             col = pal[1],
             lwd = 1,
             method = "lm",
             show.legend = F)+
  annotate(geom = "text",
           x = 600, y = 1020,
           size = 5,
           label = "R^2 == 0.98",
           parse = T)+
  scale_x_continuous(
    breaks = c(400, 600, 800, 1000),
    labels = as.integer(c(400, 600, 800, 1000) / 60)
    )+
  scale_y_continuous(
    breaks = c(400, 600, 800, 1000),
    labels = as.integer(c(400, 600, 800, 1000) / 60)
  )+
  coord_cartesian(expand = T,
  #             # xlim = c(400, 1050),
  #             ylim = c(250, 1050)
  )+
  geom_abline(slope = 1, lty = 2,
              col = "black")+
  ggthemes::theme_few()+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.minor = element_line(colour = "grey"))+
  labs(x = "inferred duration (min)",
       y = "real duration (min)")
```

@@

```{r}
# wrap together
figure_res_patch <-
wrap_plots(list(fig_basic_residence, figure_patch_duration),
           ncol = 1,
           design = "AA\nAA\nAA\nAA\nBB")+
  plot_annotation(tag_levels = "a",
                tag_prefix = "(",
                tag_suffix = ")") &
theme(plot.tag = element_text(face = "bold"))

@@

>>>>

```{r}
# read and plot example data
data <- fread("data/atlas1060_allTrials_annotated.csv")
data_raw <- copy(data)
```

```{r echo=FALSE}
# plot data
fig_data_raw <-
  ggplot(data)+
  geom_path(aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(aes(x, y),
             col = pal[3], alpha = 0.2, size = 2)+
  ggthemes::theme_map()+
  coord_sf(crs = 32631)

@@

```{r echo=FALSE}
# plot data
fig_data_bbox <-
  ggplot()+
  geom_path(data = data_raw,
            aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(data = data_raw,
             aes(x, y,
                 col = x > 645000),
             alpha = ifelse(data_raw$x > 645000, 0.5, 1),
             size = ifelse(data_raw$x > 645000, 0.3, 2),
             show.legend = F)+
  scale_colour_manual(values = c("grey", pal[3]))+
  geom_vline(xintercept = 645000,
             col = "grey", lty = 2)+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631)

@@

```{r echo=FALSE}
# plot filtered data
fig_speed_outliers <-
  ggplot()+
  geom_point(data = data,
             aes(x, y, 
                 col = speed_in < 25.6),
             size = 0.3, alpha = 0.5,
             show.legend = F)+
  scale_color_manual(values = c("grey", pal[3]))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "speed (m/s)")

@@

![](figures/fig_speed_outlier.png)

@@

```{r echo=FALSE}
# make zoomed in figures
fig_inset <- mapply(function(xl, yl) {
  ggplot()+
    geom_point(data = data_raw[!data_unproc, on = c("x", "y")],
               aes(x, y),
               col = "grey",
               shape = 4,
               size = 0.4)+
    geom_point(data = data_unproc,
               aes(x, y),
               col = pal[3],
               shape = 19, 
               alpha = 0.5)+
    geom_path(data = data,
              aes(x, y),
              col = RColorBrewer::brewer.pal(4, "Set1")[4])+
    ggthemes::theme_few()+
    theme(axis.title = element_blank(),
          axis.text = element_blank())+
    ggspatial::annotation_scale(location = "br")+
    coord_cartesian(
             xlim = xl,
             ylim = yl, expand = F
             )+
    labs(colour = "track")
}, list(xl1 = c(650785, 653250),
        xl2 = c(650045, 650682)),
   list(yl1 = c(5904450, 5906133),
        yl2 = c(5902700, 5903080)),
SIMPLIFY = FALSE)

@@

```{r echo=FALSE}
# make combined walkthrough figure
figure_walkthrough <-
wrap_plots(
  list(
    fig_data_bbox, fig_speed_outliers, fig_median_smooth),
  design = "AB\nAC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")&
  theme(plot.tag = element_text(face = "bold"))

@@

![](figures/fig_walkthrough.png)

@@

```{r echo=FALSE}
fig_calib_residence <-
  ggplot()+
  geom_point(data = data_res, 
             aes(x, y),
             size = 5, shape = 2,
             alpha = 0.1)+
  geom_point(data = data_recurse,
             aes(x, y, 
                 col = res_time > 5,
                 size = res_time > 5),
             shape = 19, alpha = 0.4,
             show.legend = F)+
  geom_path(data = data_recurse,
             aes(x, y),
            col = "grey", lwd = 0.2)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_size_manual(values = c(0.5, 2))+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631)
```

@@

We prepare a plot of the residence patches.

```{r echo=FALSE}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             # stroke = ,
             col = "grey20",
             alpha = 1)+
    # geom_path(data = data_recurse,
    #          aes(x, y),
    #         col = "grey", lwd = 0.2)+
  # geom_text(data = data_res_summary,
  #           aes(x_median, y_median,
  #               label = tID),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = 100,
  #           fontface = "bold",
  #           col = "grey20",
  #           alpha = 1)+
  # geom_text(data = patch_summary_data, 
  #           aes(x_median, y_median,
  #               label = patch),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = -50,
  #           fontface = "bold",
  #           col = pal[4],
  #           alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  # geom_segment(data = patch_summary_data,
  #           aes(x = x_end, y = y_end,
  #               xend = shift(x_start, type = "lag"),
  #               yend = shift(y_start, type = "lag")),
  #           col = pal[4], lty = 1,
  #           lwd = 0.5)+
  # geom_point(data = patch_summary_data,
  #            aes(x_median, y_median),
  #            size = 5,
  #            stroke = 1,
  #            col = pal[4],
  #            shape = 1,
  #            show.legend = F)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```

@@

```{r echo=FALSE}
# make figure comparing different methods
figure_patch_duration <-
  ggplot()+
  geom_point(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             show.legend = F,
            size = 3,
            stroke = 2,
            shape = 1,
            col = pal[2])+
  geom_smooth(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             se = F,
             col = pal[1],
             lwd = 1,
             method = "lm",
             show.legend = F)+
  annotate(geom = "text",
           x = 600, y = 1020,
           size = 5,
           label = "R^2 == 0.98",
           parse = T)+
  scale_x_continuous(
    breaks = c(400, 600, 800, 1000),
    labels = as.integer(c(400, 600, 800, 1000) / 60)
    )+
  scale_y_continuous(
    breaks = c(400, 600, 800, 1000),
    labels = as.integer(c(400, 600, 800, 1000) / 60)
  )+
  coord_cartesian(expand = T,
  #             # xlim = c(400, 1050),
  #             ylim = c(250, 1050)
  )+
  geom_abline(slope = 1, lty = 2,
              col = "black")+
  ggthemes::theme_few()+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.minor = element_line(colour = "grey"))+
  labs(x = "inferred duration (min)",
       y = "real duration (min)")
```

@@

```{r echo=FALSE}
# wrap together
figure_res_patch <-
wrap_plots(list(fig_basic_residence, figure_patch_duration),
           ncol = 1,
           design = "AA\nAA\nAA\nAA\nBB")+
  plot_annotation(tag_levels = "a",
                tag_prefix = "(",
                tag_suffix = ")") &
theme(plot.tag = element_text(face = "bold"))

@@

![](figures/fig_calib_residence_patch.png)

### 2020-10-29 06_bat_data.Rmd

---
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

```{r}
# plot bat data to examine for errors
fig_bat_raw <-
  ggplot(data)+
  geom_path(aes(X, Y,
                group = TAG,
                colour = TAG),
            show.legend = FALSE)+
  scale_colour_brewer(palette = "Dark2")+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039)
```

@@

```{r}
# save to figures
ggsave(fig_bat_raw,
       filename = "figures/fig_bat_raw.png",
       dpi = 300,
       width = 6, height = 4)
```

@@

```{r}
# now plot over raw data
fig_bat_filter_cov <- 
  ggplot()+
  geom_point(data = data[!data_split, 
                         on = c("TAG", "X", "Y", "TIME")],
             aes(X, Y),
             col = "grey",
             shape = 4)+
  geom_path(data = data_split,
             aes(X, Y,
                 col = TAG),
             size = 0.3,
             show.legend = FALSE)+
  scale_colour_brewer(palette = "Dark2")+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039,
           xlim = range(data_split$X),
           ylim = range(data_split$Y))
```

@@

```{r}
# save to figures
ggsave(fig_bat_filter_cov,
       filename = "figures/fig_bat_filter_cov.png",
       dpi = 300,
       width = 4, height = 6)
```

@@

```{r}
# now plot over raw data
fig_bat_filter_speed <-
  ggplot()+
  geom_point(data = data[!data_split, 
                         on = c("TAG", "X", "Y", "TIME")],
             aes(X, Y),
             col = "grey",
             shape = 4)+
  geom_path(data = data_split,
             aes(X, Y,
                 col = TAG),
             size = 0.3,
             show.legend = FALSE)+
  scale_colour_brewer(palette = "Dark2")+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039,
           xlim = range(data_split$X),
           ylim = range(data_split$Y))
```

@@

```{r}
# save to figures
ggsave(fig_bat_filter_speed,
       filename = "figures/fig_bat_filter_speed.png",
       dpi = 300,
       width = 4, height = 6)
```

@@

```{r}
# plot the raw, filtered, and smoothed data
fig_bat_smooth <- 
  ggplot()+
  geom_point(data = data_split,
             aes(X, Y),
             col = "grey",
             shape = 4,
             show.legend = FALSE)+
  geom_path(data = data_smooth,
            aes(X, Y,
                col = TAG),
            lwd = 0.3,
            show.legend = FALSE)+
  scale_colour_brewer(palette = "Dark2")+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039,
           xlim = range(data_smooth$X),
           ylim = range(data_smooth$Y))
```

@@

```{r}
# save to figures
ggsave(fig_bat_smooth,
       filename = "figures/fig_bat_smooth.png",
       dpi = 300,
       width = 4, height = 6)
```

@@

```{r}
fig_bat_res_timeseries <-
  ggplot()+
  geom_path(data = data_residence,
            aes(ts, resTime,
                colour = TAG),
            show.legend = F)+
  scale_color_brewer(palette = "Dark2")+
  scale_x_datetime()+
  ggthemes::theme_few()+
  labs(x = NULL,
       y = "residence time (mins)")
```

@@

```{r}
# save to figures
ggsave(fig_bat_res_timeseries,
       filename = "figures/fig_bat_res_timeseries.png",
       dpi = 300,
       width = 6, height = 3)
```

@@

>>>>

---
editor_options:
  chunk_output_type: console
output:
  pdf_document: default
  html_document: default
---

@@

```{r echo=FALSE}
# plot bat data to examine for errors
fig_bat_raw <-
  ggplot(data)+
  geom_path(aes(X, Y,
                group = TAG,
                colour = TAG),
            show.legend = FALSE)+
  scale_colour_brewer(palette = "Dark2")+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039)
```

@@

```{r echo=FALSE}
# save to figures
ggsave(fig_bat_raw,
       filename = "figures/fig_bat_raw.png",
       dpi = 300,
       width = 6, height = 4)
```

@@

```{r echo=FALSE}
# now plot over raw data
fig_bat_filter_cov <- 
  ggplot()+
  geom_point(data = data[!data_split, 
                         on = c("TAG", "X", "Y", "TIME")],
             aes(X, Y),
             col = "grey",
             shape = 4)+
  geom_path(data = data_split,
             aes(X, Y,
                 col = TAG),
             size = 0.3,
             show.legend = FALSE)+
  scale_colour_brewer(palette = "Dark2")+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039,
           xlim = range(data_split$X),
           ylim = range(data_split$Y))
```

@@

```{r echo=FALSE}
# save to figures
ggsave(fig_bat_filter_cov,
       filename = "figures/fig_bat_filter_cov.png",
       dpi = 300,
       width = 4, height = 6)
```

@@

```{r echo=FALSE}
# now plot over raw data
fig_bat_filter_speed <-
  ggplot()+
  geom_point(data = data[!data_split, 
                         on = c("TAG", "X", "Y", "TIME")],
             aes(X, Y),
             col = "grey",
             shape = 4)+
  geom_path(data = data_split,
             aes(X, Y,
                 col = TAG),
             size = 0.3,
             show.legend = FALSE)+
  scale_colour_brewer(palette = "Dark2")+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039,
           xlim = range(data_split$X),
           ylim = range(data_split$Y))
```

@@

```{r echo=FALSE}
# save to figures
ggsave(fig_bat_filter_speed,
       filename = "figures/fig_bat_filter_speed.png",
       dpi = 300,
       width = 4, height = 6)
```

@@

```{r echo=FALSE}
# plot the raw, filtered, and smoothed data
fig_bat_smooth <- 
  ggplot()+
  geom_point(data = data_split,
             aes(X, Y),
             col = "grey",
             shape = 4,
             show.legend = FALSE)+
  geom_path(data = data_smooth,
            aes(X, Y,
                col = TAG),
            lwd = 0.3,
            show.legend = FALSE)+
  scale_colour_brewer(palette = "Dark2")+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039,
           xlim = range(data_smooth$X),
           ylim = range(data_smooth$Y))
```

@@

```{r echo=FALSE}
# save to figures
ggsave(fig_bat_smooth,
       filename = "figures/fig_bat_smooth.png",
       dpi = 300,
       width = 4, height = 6)
```

@@

```{r echo=FALSE}
fig_bat_res_timeseries <-
  ggplot()+
  geom_path(data = data_residence,
            aes(ts, resTime,
                colour = TAG),
            show.legend = F)+
  scale_color_brewer(palette = "Dark2")+
  scale_x_datetime()+
  ggthemes::theme_few()+
  labs(x = NULL,
       y = "residence time (mins)")
```

@@

```{r echo=FALSE}
# save to figures
ggsave(fig_bat_res_timeseries,
       filename = "figures/fig_bat_res_timeseries.png",
       dpi = 300,
       width = 6, height = 3)
```

@@

This figure made in QGIS.
